Measuring contrast processing in the visual system using SSVEP

### 2024-04-06 review.qmd
I think figure references need to be lower case

First, we implement a simple non-linear transducer with a single input to illustrate the typical sigmoidal shape of a contrast response function [@fig-ContrastResponseFunction].

@@

One of the simplest nonlinearities is the function that describes a cell's response to different levels of contrast. In @fig-ContrastResponseFunction this is modeled as described above by a hyperbolic ratio function resulting in a saturating non-linearity:

```{python}
#| label: fig-ContrastResponseFunction
#| fig-cap: "Non-linear contrast response function resulting from the population average of two full-wave rectified signals passing through a non-linear transducer. Note the 'supersaturation' at high contrast levels."
#| fig-cap-location: bottom

@@

@@

To illustrate the effect of contrast gain control [@Heeger1992], we include a second component that contributes to the gain pool of the first. At a single pair of (matched) contrast levels, we see a complex pattern of intermodulation terms in the FT [@fig-Intermodulation].

```{python}
#| label: fig-Intermodulation
#| fig-cap: "Non-linear combination of two independent contrast modulations at F1 and F2 results in 'intermodulation' terms that appear at low-order sums and differences of those frequencies"
#| fig-cap-location: bottom

@@

Because SSVEP responses at detection threshold are very small, estimating threshold is achieved by measuring the contrast response function at relatively high levels, and extrapolating back along the function (either contrast vs response measured at a constant spatial frequency or spatial frequency vs response at a constant contrast level) to estimate its intercept with the x-axis (see @fig-SweepVEP). This contrast level was shown to correspond approximately with psychophysically measured detection thresholds [@Norcia1986].

@@

#| label: fig-SweepVEP
#| fig-cap: "Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts"
#| fig-cap-location: bottom

>>>>

First, we implement a simple non-linear transducer with a single input to illustrate the typical sigmoidal shape of a contrast response function [@fig-contrastresponsefunction].

@@

```{python}
#| label: fig-contrastresponsefunction
#| fig-cap: "Non-linear contrast response function resulting from the population average of two full-wave rectified signals passing through a non-linear transducer. Note the 'supersaturation' at high contrast levels."
#| fig-cap-location: bottom

@@

One of the simplest nonlinearities is the function that describes a cell's response to different levels of contrast. In @fig-contrastresponsefunction this is modeled as described above by a hyperbolic ratio function resulting in a saturating non-linearity:

@@

To illustrate the effect of contrast gain control [@Heeger1992], we include a second component that contributes to the gain pool of the first. At a single pair of (matched) contrast levels, we see a complex pattern of intermodulation terms in the FT [@fig-intermodulation].

```{python}
#| label: fig-intermodulation
#| fig-cap: "Non-linear combination of two independent contrast modulations at F1 and F2 results in 'intermodulation' terms that appear at low-order sums and differences of those frequencies"
#| fig-cap-location: bottom

@@

Because SSVEP responses at detection threshold are very small, estimating threshold is achieved by measuring the contrast response function at relatively high levels, and extrapolating back along the function (either contrast vs response measured at a constant spatial frequency or spatial frequency vs response at a constant contrast level) to estimate its intercept with the x-axis (see @fig-sweepvep). This contrast level was shown to correspond approximately with psychophysically measured detection thresholds [@Norcia1986].

@@

#| label: fig-sweepvep
#| fig-cap: "Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts"
#| fig-cap-location: bottom
